intro

### 2022-03-10 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update TheoreticalBackground.Rmd
Rephrased sentences to link ER flexibility/ER repertoire to ER choice and subjective values

For example, greater ER flexibility is related to reduced negative affect and therefore beneficial in daily life [@Blanke2020].
Strategies have to be chosen from the repertoire that are useful for goal achieving.

>>>>

Additionally, greater ER flexibility is related to reduced negative affect and therefore beneficial in daily life [@Blanke2020].
How do people choose strategies from their repertoire? 
Similarly to the expectancy-value model of emotion regulation <!-- Tamir et al, siehe comment oben --> it could be assumed, that people also assign a value to an ER strategy reflecting the usefulness of this strategy for goal achieving.
